---
title: "Data processing"
author: "Sean Hughes & Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes 
    toc_float: yes
---

```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE)
```

# Dependencies

```{r}

library(tidyverse)
library(readxl)
library(ggthemes)
library(knitr)
library(kableExtra)
library(IATscores)

```

# Conditions

Some experimental conditions are not recorded in the data produced by inquisit but are discerned by the file names they come from, or the presence or absence of one phase of data. Extract this here. 

```{r}

current_experiment_number <- 7

# stimulus identity using acquisition_training file names
data_stimulus_identity_condition <- 
  bind_rows(
    # acquisition_only
    read_xlsx("raw/acquisition_only/intersecting_regularities_1_no_location.xlsx") %>%
      mutate(stimulus_identity_condition = "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad",
             experiment_condition = "acquisition_only",
             subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/acquisition_only/intersecting_regularities_2_no_location.xlsx") %>%
      mutate(stimulus_identity_condition = "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad",
             experiment_condition = "acquisition_only",
             subject = paste(subject, experiment_condition, sep = "_")),
    # counterconditioning 
    read_xlsx("raw/counterconditioning/intersecting_regularities_1_no_location.xlsx") %>%
      mutate(stimulus_identity_condition = "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad",
             experiment_condition = "acquisition_and_counterconditioning",
             subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/counterconditioning/intersecting_regularities_2_no_location.xlsx") %>%
      mutate(stimulus_identity_condition = "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad",
             experiment_condition = "acquisition_and_counterconditioning",
             subject = paste(subject, experiment_condition, sep = "_")),
    # extinction only
    read_xlsx("raw/extinction/intersecting_regularities_1_no_location.xlsx") %>%
      mutate(stimulus_identity_condition = "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad",
             experiment_condition = "acquisition_and_extinction",
             subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/extinction/intersecting_regularities_2_no_location.xlsx") %>%
      mutate(stimulus_identity_condition = "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad",
             experiment_condition = "acquisition_and_extinction",
             subject = paste(subject, experiment_condition, sep = "_"))
  ) %>%
  select(subject, stimulus_identity_condition, experiment_condition) %>%
  distinct(subject, .keep_all = TRUE)

# task order
data_task_order <- 
  bind_rows(
    # acquisition_only
    read_xlsx("raw/acquisition_only/stimulus_ratings_before.xlsx") %>% 
      select(subject) %>% 
      mutate(task_order = "Explicits First",
             experiment_condition = "acquisition_only",
             subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/acquisition_only/stimulus_ratings_after.xlsx") %>% 
      select(subject) %>% 
      mutate(task_order = "Implicits First",
             experiment_condition = "acquisition_only",
             subject = paste(subject, experiment_condition, sep = "_")),
    # counterconditioning 
    read_xlsx("raw/counterconditioning/stimulus_ratings_before.xlsx") %>% 
      select(subject) %>% 
      mutate(task_order = "Explicits First",
             experiment_condition = "acquisition_and_counterconditioning",
             subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/counterconditioning/stimulus_ratings_after.xlsx") %>% 
      select(subject) %>% 
      mutate(task_order = "Implicits First",
             experiment_condition = "acquisition_and_counterconditioning",
             subject = paste(subject, experiment_condition, sep = "_")),
    # extinction only
    read_xlsx("raw/extinction/stimulus_ratings_before.xlsx") %>% 
      select(subject) %>% 
      mutate(task_order = "Explicits First",
             experiment_condition = "acquisition_and_extinction",
             subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/extinction/stimulus_ratings_after.xlsx") %>% 
      select(subject) %>% 
      mutate(task_order = "Implicits First",
             experiment_condition = "acquisition_and_extinction",
             subject = paste(subject, experiment_condition, sep = "_"))
  ) %>%
  select(-experiment_condition)

# combine
data_conditions <- data_stimulus_identity_condition %>%
  full_join(data_task_order, by = "subject") %>%
  mutate(experiment = current_experiment_number)

rm(data_stimulus_identity_condition, data_task_order)

```

# Demographics

```{r}

data_demographics <- 
  bind_rows(
    read_xlsx("raw/acquisition_only/demographics.xlsx") %>% 
      mutate(experiment_condition = "acquisition_only",
             subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/counterconditioning/demographics.xlsx") %>% 
      mutate(experiment_condition = "acquisition_and_counterconditioning",
             subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/extinction/demographics.xlsx") %>% 
      mutate(experiment_condition = "acquisition_and_extinction",
             subject = paste(subject, experiment_condition, sep = "_")),
  ) %>%
  select(subject, experiment_condition, trialcode, response) %>% 
  pivot_wider(names_from = trialcode,
              values_from = response) %>%
  mutate(gender = case_when(str_detect(tolower(gender), "f") ~ "F",
                            str_detect(tolower(gender), "female") ~ "F",
                            str_detect(tolower(gender), "m") ~ "M",
                            str_detect(tolower(gender), "male") ~ "M",
                            TRUE ~ gender)) %>%
  select(-experiment_condition)

```

# Training and testing 

## Get data and tidy

```{r}

data_training_and_testing_input <- 
  bind_rows(
    # acquisition _training 
    bind_rows(
      # acquisition_only
      read_xlsx("raw/acquisition_only/intersecting_regularities_1_no_location.xlsx") %>%
        mutate(experiment_condition = "acquisition_only",
               subject = paste(subject, experiment_condition, sep = "_")),
      read_xlsx("raw/acquisition_only/intersecting_regularities_2_no_location.xlsx") %>%
        mutate(experiment_condition = "acquisition_only",
               subject = paste(subject, experiment_condition, sep = "_")),
      # counter conditioning
      read_xlsx("raw/counterconditioning/intersecting_regularities_1_no_location.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
      read_xlsx("raw/counterconditioning/intersecting_regularities_2_no_location.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
      # extinction
      read_xlsx("raw/extinction/intersecting_regularities_1_no_location.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_")),
      read_xlsx("raw/extinction/intersecting_regularities_2_no_location.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_"))
    ) %>%
      mutate(phase = "acquisition_training",
             blocknum = blocknum-3,
             response = as.character(response)),
    
    # acquisition test 
    bind_rows(
      # acquisition_only 
      read_xlsx("raw/acquisition_only/testing1_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_only",
               subject = paste(subject, experiment_condition, sep = "_")),
      read_xlsx("raw/acquisition_only/testing2_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_only",
               subject = paste(subject, experiment_condition, sep = "_")),
      # counterconditioning 
      read_xlsx("raw/counterconditioning/testing1_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
      read_xlsx("raw/counterconditioning/testing2_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
      # extinction 
      read_xlsx("raw/extinction/testing1_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_")),
      read_xlsx("raw/extinction/testing2_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_"))
    ) %>%
      mutate(phase = "acquisition_testing",
             response = as.character(response)),
    
    # counterconditioning_training
    bind_rows(
      read_xlsx("raw/counterconditioning/counterconditioning1b_no_location.xlsx") %>%
        mutate(response = as.character(response),
               experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
      read_xlsx("raw/counterconditioning/counterconditioning2b_no_location.xlsx") %>%
        mutate(response = as.character(response),
               experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_"))
    ) %>%
      mutate(phase = "counterconditioning_training") %>%
      select(-starts_with("stimulus")),
    
    # counterconditioning_testing
    bind_rows(
      read_xlsx("raw/counterconditioning/testing_counterconditioning1b_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
      read_xlsx("raw/counterconditioning/testing_counterconditioning2b_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_"))
    ) %>%
      mutate(phase = "counterconditioning_testing",
             response = as.character(response)),
    
    # extinction training 
    bind_rows(
      read_xlsx("raw/extinction/extinction_1c_no_location.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_")),
      read_xlsx("raw/extinction/extinction_2c_no_location.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_"))
    ) %>%
      mutate(phase = "extinction_training",
             blocknum = blocknum-3,
             response = as.character(response)),
    
    # extinction testing
    bind_rows(
      read_xlsx("raw/extinction/testing_extinction1c_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_")),
      read_xlsx("raw/extinction/testing_extinction2c_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_"))
    ) %>%
      mutate(phase = "extinction_testing",
             response = as.character(response))
  ) %>%
  filter(blockcode != "Begin") %>% 
  select(subject, experiment_condition, phase, block_number = blocknum, trial_number = trialnum, correct) %>%
  arrange(subject, phase) %>%
  # many participants have block numbers 5+ for some reason I don't understand. trim this data.
  filter(block_number %in% c(1, 2, 3, 4))

```

## Completeness

```{r}

# # check n participants with different n trials per phase and block 
# temp <- data_training_and_testing_input %>%
#   group_by(subject, phase, block_number) %>%
#   summarize(n = n()) %>%
#   ungroup() %>%
#   count(phase, block_number, n) %>%
#   rename(n_trials = n, n_participants = nn) %>%
#   arrange(phase, block_number, desc(n_participants))

data_training_and_testing_completeness_temp <- data_training_and_testing_input %>%
  group_by(subject, phase) %>%
  summarize(n = n()) %>%
  mutate(complete_training_testing_data = 
           case_when((phase == "acquisition_training" & n == 80) |  
                       (phase == "acquisition_testing" & n == 8) |
                       (phase == "counterconditioning_training" & n == 80) |  
                       (phase == "counterconditioning_testing" & n == 8) |  
                       (phase == "extinction_training" & n == 80) |  
                       (phase == "extinction_testing" & n == 8) ~ "complete",
                     (phase == "acquisition_training" & n > 80) |  
                       (phase == "acquisition_testing" & n > 8) |
                       (phase == "counterconditioning_training" & n > 80) |  
                       (phase == "counterconditioning_testing" & n > 8) |  
                       (phase == "extinction_training" & n > 80) |  
                       (phase == "extinction_testing" & n > 8) ~ "excess",
                     (phase == "acquisition_training" & n < 80) |  
                       (phase == "acquisition_testing" & n < 8) |
                       (phase == "counterconditioning_training" & n < 80) |  
                       (phase == "counterconditioning_testing" & n < 8) |  
                       (phase == "extinction_training" & n < 80) |  
                       (phase == "extinction_testing" & n < 8) ~ "partial")) %>%
  ungroup() %>%
  select(-n) 

data_training_and_testing_completeness_temp %>%
  count(phase, complete_training_testing_data) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

data_training_and_testing_completeness <- data_training_and_testing_completeness_temp %>%
  pivot_wider(names_from = phase, 
              values_from = complete_training_testing_data,
              names_prefix = "completeness_")

```

## Performance

```{r}

data_training_and_testing_performance_temp <- data_training_and_testing_input %>%
  # summarize performance by block
  group_by(subject, phase, block_number) %>% 
  summarise(mean_correct = mean(correct), 
            sd_correct = sd(correct)) %>%
  mutate(passed_performance_criterion_by_block = ifelse(mean_correct < .75, FALSE, TRUE)) %>%
  ungroup() %>% 
  # summarize performance by participant (final block only)
  group_by(subject, phase) %>% 
  mutate(passed_performance_criterion = ifelse(block_number == max(block_number) & passed_performance_criterion_by_block == TRUE, TRUE, FALSE)) %>%
  ungroup() %>%
  mutate(phase = fct_relevel(phase,
                             "extinction_testing",
                             "extinction_training",
                             "counterconditioning_testing",
                             "counterconditioning_training",
                             "acquisition_testing",
                             "acquisition_training")) %>%
  drop_na()

# plot
data_training_and_testing_performance_temp %>% 
  group_by(phase, block_number, passed_performance_criterion_by_block) %>% 
  summarise(mean_accuracy = mean(mean_correct), sd_accuracy = sd(sd_correct)) %>%
  ggplot(aes(x=block_number, y=mean_accuracy, fill = passed_performance_criterion_by_block)) +
  geom_bar(colour="black", stat="identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin=mean_accuracy-sd_accuracy, ymax=mean_accuracy+sd_accuracy), width=.2,
                position=position_dodge(.9)) + theme_classic() +
  facet_wrap(~phase, ncol = 1)

data_training_and_testing_performance <- data_training_and_testing_performance_temp %>%
  group_by(subject, phase) %>% 
  filter(block_number == max(block_number)) %>%
  ungroup() %>%
  select(-block_number, -passed_performance_criterion_by_block, -sd_correct) %>%
  pivot_wider(names_from = phase,
              values_from = c(mean_correct, passed_performance_criterion))

```

- NB because the last block each participant completes is selected, if participants have partial data, their means refer to their last completed block not the ultimate block. therefore ensure that partial data exclusions are done.

# Manipulation check

```{r}

data_manipulation_check <- 
  bind_rows(
    read_xlsx("raw/acquisition_only/manipulation_check_instructions.xlsx") %>%
        mutate(experiment_condition = "acquisition_only",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/counterconditioning/manipulation_check_instructions.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/extinction/manipulation_check_instructions.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_"))
  ) %>%
  select(subject, manipulation_check_response = testquestion_Instruction_response) %>%
  mutate(passed_manipulation_check = ifelse(manipulation_check_response == "I have to click on the specific letter that goes with the image I see", TRUE, FALSE)) %>%
  select(subject, passed_manipulation_check)

data_manipulation_check %>%
  count(passed_manipulation_check) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Self-reports

```{r}

data_demand <- 
  bind_rows(
    read_xlsx("raw/acquisition_only/demand.xlsx") %>%
        mutate(experiment_condition = "acquisition_only",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/counterconditioning/demand.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/extinction/demand.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_"))
  ) %>% 
  mutate(demand_response = case_when(Demand_response == "What I learned during the experiment" ~ "Not Demand Compliant",
                                     Demand_response == "I don't know why I evaluated the items as I did" ~ "Not Demand Compliant",
                                     Demand_response == "What I learned during the experiment" ~ "Not Demand Compliant",
                                     Demand_response == "What I thought the experimenter wanted me to say" ~ "Demand Compliant",
                                     Demand_response == "I based my ratings on some some factor that was not what I learned or what the experimenter wanted me to do" ~ "Not Demand Compliant")) %>%
  select(subject, demand_response)

data_reactance <- 
  bind_rows(
    read_xlsx("raw/acquisition_only/reactance.xlsx") %>%
        mutate(experiment_condition = "acquisition_only",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/counterconditioning/reactance.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/extinction/reactance.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_"))
  ) %>% 
  select(subject, 
         reactance_response_1 = react1_response, 
         reactance_response_2 = react2_response) %>%
  mutate(reactance_response_2 = str_remove_all(reactance_response_2, "[^0-9]"))

# # no believability in this study
# data_believability <- read_xlsx("raw/acquisition_only/cover_belief.xlsx") %>% 
#   select(subject, 
#          believability_response_1 = belief1_response, 
#          believability_response_2 = belief2_response) %>%
#   mutate(believability_response_2 = str_remove_all(believability_response_2, "[^0-9]"))

data_confidence_ratings <- 
  bind_rows(
    read_xlsx("raw/acquisition_only/confidence_ratings.xlsx") %>%
        mutate(experiment_condition = "acquisition_only",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/counterconditioning/confidence_ratings.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/extinction/confidence_ratings.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_"))
  ) %>% 
  select(subject, 
         confidence_stim_1 = Stimulus_1_Confidence_Confidence_response, 
         confidence_stim_2 = Stimulus_2_Confidence_Confidence_response, 
         confidence_stim_3 = Stimulus_3_Confidence_Confidence_response, 
         confidence_stim_4 = Stimulus_4_Confidence_Confidence_response)

data_ratings <- 
  bind_rows(
    read_xlsx("raw/acquisition_only/valence_ratings.xlsx") %>%
        mutate(experiment_condition = "acquisition_only",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/counterconditioning/valence_ratings.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/extinction/valence_ratings.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_"))
  ) %>% 
  select(subject, 
         Outcome_1_Pos_Neg = Stimulus_1_Positive_Negative_Positive_Negative_response,
         Outcome_1_Good_Bad = Stimulus_1_Good_Bad_Good_Bad_response,
         Outcome_1_Pleasant_Unpleasant = Stimulus_1_Pleasant_Unpleasant_Pleasant_Unpleasant_response,
         Outcome_1_Like_Dislike = Stimulus_1_Like_Dislike_Like_Dislike_response,
         Outcome_2_Pos_Neg = Stimulus_3_Positive_Negative_Positive_Negative_response,
         Outcome_2_Good_Bad = Stimulus_3_Good_Bad_Good_Bad_response, 
         Outcome_2_Pleasant_Unpleasant = Stimulus_3_Pleasant_Unpleasant_Pleasant_Unpleasant_response,
         Outcome_2_Like_Dislike = Stimulus_3_Like_Dislike_Like_Dislike_response,
         Target_1_Pos_Neg = Stimulus_2_Positive_Negative_Positive_Negative_response,
         Target_1_Good_Bad = Stimulus_2_Good_Bad_Good_Bad_response, 
         Target_1_Pleasant_Unpleasant = Stimulus_2_Pleasant_Unpleasant_Pleasant_Unpleasant_response,
         Target_1_Like_Dislike = Stimulus_2_Like_Dislike_Like_Dislike_response,
         Target_2_Pos_Neg = Stimulus_4_Positive_Negative_Positive_Negative_response,
         Target_2_Good_Bad = Stimulus_4_Good_Bad_Good_Bad_response,
         Target_2_Pleasant_Unpleasant = Stimulus_4_Pleasant_Unpleasant_Pleasant_Unpleasant_response,
         Target_2_Like_Dislike = Stimulus_4_Like_Dislike_Like_Dislike_response) %>% 
  # Create a mean rating score for each stimulus
  # Create an operant evaluative conditioning (OEC) and intersecting regularites (IR) effect
  rowwise() %>%
  mutate(mean_outcome_1 = mean(c(Outcome_1_Pos_Neg, Outcome_1_Good_Bad, Outcome_1_Pleasant_Unpleasant, Outcome_1_Like_Dislike)),
         mean_outcome_2 = mean(c(Outcome_2_Pos_Neg, Outcome_2_Good_Bad, Outcome_2_Pleasant_Unpleasant, Outcome_2_Like_Dislike)),
         mean_target_1  = mean(c(Target_1_Pos_Neg, Target_1_Good_Bad, Target_1_Pleasant_Unpleasant, Target_1_Like_Dislike)),
         mean_target_2  = mean(c(Target_2_Pos_Neg, Target_2_Good_Bad, Target_2_Pleasant_Unpleasant, Target_2_Like_Dislike)),
         self_reported_OEC_effect     = mean_outcome_1 - mean_outcome_2,
         self_reported_IR_effect      = mean_target_1 - mean_target_2) %>%
  ungroup() %>%
  select(subject, self_reported_OEC_effect, self_reported_IR_effect)

# behavioural intentions
data_intentions <- 
  bind_rows(
    full_join(read_xlsx("raw/acquisition_only/intention_ratings_1_3.xlsx") %>%
                mutate(experiment_condition = "acquisition_only",
                       subject = paste(subject, experiment_condition, sep = "_")) %>%
                select(subject, behavioral_intentions_OEC = Intentions_1_3_response),
              read_xlsx("raw/acquisition_only/intention_ratings_2_4.xlsx") %>%
                mutate(experiment_condition = "acquisition_only",
                       subject = paste(subject, experiment_condition, sep = "_")) %>%
                select(subject, behavioral_intentions_IR = Intentions_2_4_response),
              by = "subject"),
    full_join(read_xlsx("raw/counterconditioning/intention_ratings_1_3.xlsx") %>%
                mutate(experiment_condition = "acquisition_and_counterconditioning",
                       subject = paste(subject, experiment_condition, sep = "_")) %>%
                select(subject, behavioral_intentions_OEC = Intentions_1_3_response),
              read_xlsx("raw/counterconditioning/intention_ratings_2_4.xlsx") %>%
                mutate(experiment_condition = "acquisition_and_counterconditioning",
                       subject = paste(subject, experiment_condition, sep = "_")) %>%
                select(subject, behavioral_intentions_IR = Intentions_2_4_response),
              by = "subject"),
    full_join(read_xlsx("raw/extinction/intention_ratings_1_3.xlsx") %>%
                mutate(experiment_condition = "acquisition_and_extinction",
                       subject = paste(subject, experiment_condition, sep = "_")) %>%
                select(subject, behavioral_intentions_OEC = Intentions_1_3_response),
              read_xlsx("raw/extinction/intention_ratings_2_4.xlsx") %>%
                mutate(experiment_condition = "acquisition_and_extinction",
                       subject = paste(subject, experiment_condition, sep = "_")) %>%
                select(subject, behavioral_intentions_IR = Intentions_2_4_response),
              by = "subject")
  )
    
```

# IAT

## Tidying

```{r}

data_iat_input <- 
  bind_rows(
    # acquisition_phase
    read_xlsx("raw/acquisition_only/iat_symbols_before.xlsx") %>%
      mutate(experiment_condition = "acquisition_only",
             subject = paste(subject, experiment_condition, sep = "_"),
             task_order = "iat before explicits",
             response = as.character(response)),
    read_xlsx("raw/acquisition_only/iat_symbols_after.xlsx") %>%
      mutate(experiment_condition = "acquisition_only",
             subject = paste(subject, experiment_condition, sep = "_"),
             task_order = "iat after explicits",
             response = as.character(response)),
    # counterconditioning
    read_xlsx("raw/counterconditioning/iat_symbols_before.xlsx") %>%
      mutate(experiment_condition = "acquisition_and_counterconditioning",
             subject = paste(subject, experiment_condition, sep = "_"),
             task_order = "iat before explicits",
             response = as.character(response)),
    read_xlsx("raw/counterconditioning/iat_symbols_after.xlsx") %>%
      mutate(experiment_condition = "acquisition_and_counterconditioning",
             subject = paste(subject, experiment_condition, sep = "_"),
             task_order = "iat after explicits",
             response = as.character(response)),
    # extinction
    read_xlsx("raw/extinction/iat_symbols_before.xlsx") %>%
      mutate(experiment_condition = "acquisition_and_extinction",
             subject = paste(subject, experiment_condition, sep = "_"),
             task_order = "iat before explicits",
             response = as.character(response)),
    read_xlsx("raw/extinction/iat_symbols_after.xlsx") %>%
      mutate(experiment_condition = "acquisition_and_extinction",
             subject = paste(subject, experiment_condition, sep = "_"),
             task_order = "iat after explicits",
             response = as.character(response))
  ) %>%
  mutate(experiment = current_experiment_number) %>%
  select(subject, experiment, 
         block_type = blockcode, block = blocknum, trial_number = trialnum, 
         correct, latency) %>%
  mutate(trial_number = ifelse(block %in% c(1, 2, 3, 6, 7), trial_number-1, trial_number)) %>%
  # the number of the blocks is incorrect due to the way the task was coded, recode
  mutate(block = case_when(block == 1 ~ 1,
                           block == 2 ~ 2,
                           block == 3 ~ 3,
                           block == 5 ~ 4,
                           block == 6 ~ 5,
                           block == 7 ~ 6,
                           block == 9 ~ 7))

# block order
data_iat_block_order <- data_iat_input %>%
  filter(block == 1 & trial_number == 1) %>%
  mutate(iat_block_order = case_when(block_type == "targetincompatiblepractice" ~ "learning_inconsistent_first",
                                     block_type == "targetcompatiblepractice" ~ "learning_consistent_first")) %>%
  select(subject, iat_block_order)

# only retain the critical practice and test blocks (i.e., block_number = 3, 4, 6, 7)
data_iat_cleaned <- data_iat_block_order %>%
  left_join(data_iat_input, by = "subject") %>% 
  filter(block %in% c(3, 4, 6, 7))

```

## Completeness

```{r}

data_iat_completeness <- data_iat_cleaned %>%
  group_by(subject) %>%
  summarize(n = n()) %>%
  mutate(complete_iat_data = case_when(n == 120 ~ "complete", 
                                       n > 120 ~ "excess", 
                                       n < 120 ~"partial")) %>%
  ungroup() %>%
  select(-n)

data_iat_completeness %>%
  distinct(subject, .keep_all = TRUE) %>%
  count(complete_iat_data) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

## Performance

```{r}

# exclude if total error rate > 30% 
data_iat_accuracy_overall <- data_iat_cleaned %>% 
  group_by(subject) %>% 
  summarise(iat_accuracy_overall = sum(correct)/n()) %>%
  ungroup() %>%
  mutate(passed_iat_accuracy_overall = ifelse(iat_accuracy_overall >= .70, TRUE, FALSE)) %>%
  select(subject, passed_iat_accuracy_overall)

# exclude if error rate on any one block > 40% 
data_iat_accuracy_by_block <- data_iat_cleaned %>% 
  group_by(subject, block) %>% 
  summarise(iat_accuracy_by_block = sum(correct)/n()) %>%
  ungroup() %>%
  mutate(passed_iat_accuracy_by_block = ifelse(iat_accuracy_by_block >= .60, TRUE, FALSE)) %>%
  group_by(subject) %>%
  summarize(passed_iat_accuracy_by_block = as.logical(min(passed_iat_accuracy_by_block))) %>%
  ungroup()

data_iat_fast_responding <- data_iat_cleaned %>% 
  mutate(fast_response = ifelse(latency < 300, 1, 0)) %>%
  group_by(subject) %>% 
  summarise(iat_percent_fast_responses = sum(fast_response)/n()) %>%
  ungroup() %>%
  mutate(passed_iat_percent_fast_responses = ifelse(iat_percent_fast_responses <= .10, TRUE, FALSE)) %>%
  select(subject, passed_iat_percent_fast_responses)

data_iat_performance <- data_iat_accuracy_overall %>%
  full_join(data_iat_accuracy_by_block, by = "subject") %>%
  full_join(data_iat_fast_responding, by = "subject") %>%
  rowwise() %>%
  mutate(passed_iat_performance = as.logical(min(c(passed_iat_accuracy_overall, 
                                                   passed_iat_accuracy_by_block,   
                                                   passed_iat_percent_fast_responses), na.rm = TRUE))) %>%
  ungroup() %>%
  select(subject, passed_iat_performance)

rm(data_iat_accuracy_overall, data_iat_accuracy_by_block, data_iat_fast_responding)

```

## D2 scoring

```{r}

## rename and recode to create the input format that the IATscores package requires

# create a numberic version of subject
data_iat_subject_numeric <- data_iat_cleaned %>%
  distinct(subject) %>%
  rownames_to_column(var = "subject_numeric") %>%
  mutate(subject_numeric = as.numeric(subject_numeric))

data_iat_D2_scores <- data_iat_subject_numeric %>%
  left_join(data_iat_cleaned, by = "subject") %>%
  # do other wrangling
  mutate(praccrit = ifelse(block_type == "incompatibletest1" | block_type == "compatibletest1", 
                           "prac", "crit"),
         blockcode = ifelse(block_type == "incompatibletest1" | block_type == "incompatibletest2",
                            "incompatible_block", "compatible_block")) %>%
  select(subject_original = subject, subject = subject_numeric, 
         block, correct, latency, praccrit,  trial_number, block_type) %>%
  mutate(blockcode = ifelse(block %in% c(3, 4), "pair1", 
                            ifelse(block %in% c(6, 7), "pair2", NA)),
         praccrit = ifelse(block %in% c(3, 6), "prac", 
                           ifelse(block %in% c(4, 7), "crit", NA)))  %>%
  filter(!is.na(blockcode)) %>%
  # calculate D2 scores
  # parameters are identical to those the package lists in the D2 wrapper function
  IATscores::RobustScores(IATdata = .,
                          P1 = "fxtrim",  # Trim values < 400ms
                          P2 = "ignore",  # do not trim errors
                          P3 = "dscore",  # calculate d2 scores
                          P4 = "dist",    # distinguish between the prac and test blocks
                          verbose = FALSE,
                          autoremove = FALSE) %>%
  rename(IAT_D2_controlling_stimulus_identity = p2112,
         subject_numeric = subject) %>%
  full_join(data_iat_subject_numeric, by = "subject_numeric") %>%
  select(-subject_numeric)

```

# Equivalence test

This task was included in the study in an exploratory manner and was not used in the preregistered analyses or reported in the manuscript.

```{r}

data_equivalence <- 
  bind_rows(
    # acquisition_only
    read_xlsx("raw/acquisition_only/equivalencetest1_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_only",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/acquisition_only/equivalencetest2_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_only",
               subject = paste(subject, experiment_condition, sep = "_")),
    # counterconditioning
    read_xlsx("raw/counterconditioning/equivalencetest1_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/counterconditioning/equivalencetest2_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_counterconditioning",
               subject = paste(subject, experiment_condition, sep = "_")),
    # extinction
    read_xlsx("raw/extinction/equivalencetest1_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_")),
    read_xlsx("raw/extinction/equivalencetest2_nokeylocation.xlsx") %>%
        mutate(experiment_condition = "acquisition_and_extinction",
               subject = paste(subject, experiment_condition, sep = "_"))
  ) %>%
  select(subject, correct) %>%
  
  group_by(subject) %>%
  summarize(n = n(), # check completeness
            passsed_equivalence = ifelse(mean(correct) > .75, TRUE, FALSE)) %>%
  ungroup() %>%
  mutate(complete_equivalence_data = ifelse(n == 24, TRUE, FALSE)) %>%
  select(subject, complete_equivalence_data, passsed_equivalence)

data_equivalence %>%
  count(complete_equivalence_data, passsed_equivalence) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Combine and write to disk

```{r}

data_processed <- data_conditions %>%
  full_join(data_demographics, by = "subject") %>%
  full_join(data_manipulation_check, by = "subject") %>%
  full_join(data_training_and_testing_completeness, by = "subject") %>%
  full_join(data_training_and_testing_performance, by = "subject") %>%
  full_join(data_ratings, by = "subject") %>%
  full_join(data_iat_block_order, by = "subject") %>%
  full_join(data_iat_completeness, by = "subject") %>%
  full_join(data_iat_performance, by = "subject") %>%
  full_join(data_iat_D2_scores, by = "subject") %>%
  full_join(data_intentions, by = "subject") %>%
  full_join(data_equivalence, by = "subject") %>%
  full_join(data_demand, by = "subject") %>%
  full_join(data_reactance, by = "subject") %>%
  full_join(data_confidence_ratings, by = "subject") %>%
  #full_join(data_believability, by = "subject") %>%  # not present in this study
  # reverse-score the scores the self-reports based on stimulus_identity_condition
  mutate(
    self_reported_OEC_effect_controlling_stimulus_identity = case_when(
      stimulus_identity_condition == "Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good" ~ self_reported_OEC_effect*-1,
      stimulus_identity_condition == "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad" ~ self_reported_OEC_effect
    ),
    self_reported_IR_effect_controlling_stimulus_identity = case_when(
      stimulus_identity_condition == "Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good" ~ self_reported_IR_effect*-1,
      stimulus_identity_condition == "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad" ~ self_reported_IR_effect
    )
  ) %>%
  # reverse score IAT so that a positive IAT score indicates that people preferred the Target that was related to the Positive Source more than the Target related to the Negative source and vice versa
  mutate(
    IAT_D2 = case_when(
      stimulus_identity_condition == "Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good" ~ IAT_D2_controlling_stimulus_identity*-1, 
      stimulus_identity_condition == "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad" ~ IAT_D2_controlling_stimulus_identity
    )
  ) %>%
  # make unique id
  mutate(unique_id = paste(experiment, subject, sep = "_")) %>%
  # select and reorder variables
  select(experiment, 
         unique_id, 
         age, 
         gender, 
         stimulus_identity_condition, 
         experiment_condition,
         task_order, 
         passed_manipulation_check,
         
         completeness_acquisition_training, completeness_acquisition_testing, 
         completeness_counterconditioning_training, completeness_counterconditioning_testing,
         completeness_extinction_training, completeness_extinction_testing,
         
         mean_correct_acquisition_training, 
         mean_correct_counterconditioning_training, mean_correct_acquisition_testing, 
         mean_correct_extinction_training, mean_correct_extinction_testing, 
         
         passed_performance_criterion_acquisition_training, passed_performance_criterion_acquisition_testing, 
         passed_performance_criterion_counterconditioning_training, passed_performance_criterion_counterconditioning_testing,
         passed_performance_criterion_extinction_training, passed_performance_criterion_extinction_testing,
         
         self_reported_OEC_effect, self_reported_OEC_effect_controlling_stimulus_identity, 
         self_reported_IR_effect, self_reported_IR_effect_controlling_stimulus_identity, 
         complete_iat_data, 
         iat_block_order,
         passed_iat_performance,
         IAT_D2, IAT_D2_controlling_stimulus_identity, 
         behavioral_intentions_OEC, behavioral_intentions_IR,
         complete_equivalence_data, passsed_equivalence,
         demand_response, 
         reactance_response_1, reactance_response_2, 
         confidence_stim_1, confidence_stim_2, confidence_stim_3, confidence_stim_4)
         #believability_response_1, believability_response_2)  # not present in this study

# Ensures that the processed data folder exists
dir.create("processed")

# write to disk
write_csv(data_processed, "processed/data_processed.csv")

```


