---
title: "IR, extinction, & counter conditioning"
subtitle: "Analyses & meta-analyses"
author: "Ian Hussey & Sean Hughes"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes 
    toc_float: yes
---

```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE)
```

# Dependencies

```{r}

library(tidyverse)
library(ggthemes)
library(knitr)
library(kableExtra)
library(broom)
library(effsize)

# round p value using apa format
apa_p_value <- function(p){
  p_formatted <- ifelse(p >= 0.0001, paste("=", round(p, 4)),
                        ifelse(p < 0.0001, "< .0001", NA))
  p_formatted <- gsub(pattern = "0.", replacement = ".", x = p_formatted, fixed = TRUE)
  p_formatted
}

```

# Data and exclusions

 for sensitivity analyses later:
passed_performance_criterion_acquisition_training == TRUE &
passed_performance_criterion_acquisition_testing == TRUE &

```{r}

data_processed <-
  bind_rows(
    read_csv("../data/Study 1/processed/data_processed.csv"),
    read_csv("../data/Study 2/processed/data_processed.csv"),
    read_csv("../data/Study 3/processed/data_processed.csv"),
    read_csv("../data/Study 4/processed/data_processed.csv"),
    read_csv("../data/Study 5/processed/data_processed.csv"),
    read_csv("../data/Study 6/processed/data_processed.csv"),
    read_csv("../data/Study 7/processed/data_processed.csv")
  ) %>%
  # exclusions
  filter(completeness_acquisition_training == "complete" &
           completeness_acquisition_testing == "complete" &
           (completeness_extinction_training == "complete" | is.na(completeness_extinction_training)) &
           (completeness_extinction_testing == "complete" | is.na(completeness_extinction_testing)) &
           (completeness_counterconditioning_training == "complete" | is.na(completeness_counterconditioning_training)) &
           (completeness_counterconditioning_testing == "complete" | is.na(completeness_counterconditioning_testing)) &
           complete_iat_data == "complete" &
           passed_iat_performance == TRUE) %>%
  # set factor levels for t test comparisons
  mutate(experiment_condition = fct_relevel(experiment_condition,
                                            "acquisition_only", 
                                            "acquisition_and_extinction",
                                            "acquisition_and_counterconditioning"),
         stimulus_identity_condition = fct_relevel(experiment_condition,
                                            "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad",
                                            "Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good")) %>%
  
  # for testing
  filter(experiment_condition %in% c("acquisition_only", "acquisition_and_extinction") & 
           experiment %in% c(1,2,3,4,7))

```

# Analysis by study

workflow returns mean_reference and mean_comparison, where reference is the first factor level and comparison is the next highest level.

```{r}

# calculate cohens d and return its output in tidy format - a helper function for analysis_workflow
tidy_cohens_d <- function(data, DV, IV){
  require(effsize)
  
  fit <- effsize::cohen.d(DV ~ IV, data = data)
  
  results <- tibble(cohens_d = fit$estimate,
                    cohens_d_ci_lower = fit$conf.int["lower"],
                    cohens_d_ci_upper = fit$conf.int["upper"])
  
  return(results)
}




# full analysis workflow
analysis_workflow <- function(data, DV, IV){
  
  # t test
  results_t_test <- data %>%
    group_by(experiment) %>%
    do(broom::tidy(t.test(DV ~ IV, data = .))) %>%
    ungroup() %>%
    rename(t = statistic,
           df = parameter,
           p = p.value,
           mean_reference = estimate1,
           mean_comaprison = estimate2)
  
  # cohens d
  results_cohens_d <- data %>%
    group_by(experiment) %>%
    do(tidy_cohens_d(data = .))
  
  # combine
  results <- 
    full_join(results_t_test,
              results_cohens_d,
              by = "experiment") %>%
    select(experiment, mean_reference, mean_comaprison, t, df, p, cohens_d, cohens_d_ci_lower, cohens_d_ci_upper) %>%
    mutate(reportable_result = paste0("Reference group M = ", round(mean_reference, 2), ", comparison group M = ", round(mean_comaprison, 2), ", t(", round(df, 2), ") = ", round(t, 2), ", p ", apa_p_value(p), ", d = ", round(cohens_d, 2), ", 95% CI [", round(cohens_d_ci_lower, 2), ", ", round(cohens_d_ci_upper, 2), "]"))
  
  return(results)
}


# examples
temp <- data_processed %>%
  rename(DV = IAT_D2_controlling_stimulus_identity, 
         IV = experiment_condition) %>%
  analysis_workflow()


data_processed %>%
  rename(DV = IAT_D2, 
         IV = stimulus_identity_condition) %>%
  analysis_workflow()

```

# to do

- add BF
- handle between study differences
- extend to other DVs
- separate workflow for intentions (multinominal logistic)
- add metas
  - sensitivity analyses for training and testing exclusions
- add anova for study 7
- plot training and testing data







