---
title: "Data processing"
author: "Sean Hughes & Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes 
    toc_float: yes
---

```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE)
```

# Dependencies

```{r}

library(tidyverse)
library(readxl)
library(ggthemes)
library(knitr)
library(kableExtra)
library(IATscores)

```

# Conditions

Some experimental conditions are not recorded in the data produced by inquisit but are discerned by the file names they come from, or the presence or absence of one phase of data. Extract this here. 

```{r}

current_experiment_number <- 4

# stimulus identity using acquisition_training file names
data_stimulus_identity_condition <- 
  bind_rows(
    read_xlsx("raw/intersecting_regularities_left.xlsx") %>%
      mutate(stimulus_identity_condition = "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad"),
    read_xlsx("raw/intersecting_regularities_right.xlsx") %>%
      mutate(stimulus_identity_condition = "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad"),
    read_xlsx("raw/intersecting_regularities_left_rev.xlsx") %>%
      mutate(stimulus_identity_condition = "Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good"),
    read_xlsx("raw/intersecting_regularities_right_rev.xlsx") %>%
      mutate(stimulus_identity_condition = "Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good")
  ) %>%
  select(subject, stimulus_identity_condition) %>%
  distinct(subject, .keep_all = TRUE)

# stimulus identity using presence of extinction phase files
data_experiment_condition <- 
    #_extinction training
    read_xlsx("raw/extinction_intersecting_regularities_1d.xlsx") %>% 
      mutate(response = as.character(response)) %>%
  mutate(experiment_condition = "acquisition and extinction") %>%
  select(subject, experiment_condition) %>%
  distinct(subject, .keep_all = TRUE)

# task order
data_task_order <- 
  bind_rows(read_xlsx("raw/stimulus_ratings_before.xlsx") %>% 
              select(subject) %>% 
              mutate(task_order = "Explicits First"),
            read_xlsx("raw/stimulus_ratings_after.xlsx") %>% 
              select(subject) %>% 
              mutate(task_order = "Implicits First"))

# combine
data_conditions <- data_stimulus_identity_condition %>%
  full_join(data_experiment_condition, by = "subject") %>%
  full_join(data_task_order, by = "subject") %>%
  mutate(experiment = current_experiment_number,
         experiment_condition = ifelse(is.na(experiment_condition), "acquisition only", experiment_condition))

rm(data_stimulus_identity_condition, data_experiment_condition, data_task_order)

```

# Demographics

```{r}

data_demographics <- read_xlsx("raw/demographics.xlsx") %>%
  select(subject, trialcode, response) %>% 
  pivot_wider(names_from = trialcode,
              values_from = response) %>%
  mutate(gender = case_when(str_detect(tolower(gender), "f") ~ "F",
                            str_detect(tolower(gender), "female") ~ "F",
                            str_detect(tolower(gender), "m") ~ "M",
                            str_detect(tolower(gender), "male") ~ "M",
                            TRUE ~ gender)) 

```

# Training and testing 

## Get data and tidy

```{r}
data_training_and_testing_input <-
data_training_and_testing_input <- 
  bind_rows(
    # acquisition_training 
    bind_rows(
      read_xlsx("raw/intersecting_regularities_left.xlsx"),
      read_xlsx("raw/intersecting_regularities_right.xlsx"),
      read_xlsx("raw/intersecting_regularities_left_rev.xlsx"),
      read_xlsx("raw/intersecting_regularities_right_rev.xlsx")
    ) %>%
      mutate(phase = "acquisition_training",
             blocknum = blocknum-1,
             response = as.character(response)),
    
    # acquisition test 
    bind_rows(
      read_xlsx("raw/testing_left.xlsx"),
      read_xlsx("raw/testing_left_rev.xlsx"),
      read_xlsx("raw/testing_right.xlsx"),
      read_xlsx("raw/testing_right_rev.xlsx")
    ) %>%
      mutate(phase = "acquisition_testing",
             response = as.character(response)),
    
    # extinction_training
    bind_rows(
      read_xlsx("raw/extinction_intersecting_regularities_1d.xlsx")
    ) %>%
      mutate(phase = "extinction_training",
             response = as.character(response)) %>%
      select(-starts_with("stimulus")),
    
    # extinction test 
    bind_rows(
      read_xlsx("raw/testing_left.xlsx"),
      read_xlsx("raw/testing_left_rev.xlsx"),
      read_xlsx("raw/testing_right.xlsx"),
      read_xlsx("raw/testing_right_rev.xlsx")
    ) %>%
      mutate(phase = "extinction_testing",
             response = as.character(response))
  ) %>%
  filter(blockcode != "Begin") %>% 
  select(subject, phase, block_number = blocknum, trial_number = trialnum, correct) %>%
  arrange(subject, phase)

```

## Completeness

```{r}

data_training_and_testing_completeness_temp <- data_training_and_testing_input %>%
  group_by(subject, phase) %>%
  summarize(n = n()) %>%
  mutate(complete_training_testing_data = 
           case_when((phase == "acquisition_training" & n == 80) |
                       (phase == "acquisition_testing" & n == 8) |
                       (phase == "extinction_training" & n == 80) |
                       (phase == "extinction_testing" & n == 8) ~ "complete", 
                     (phase == "acquisition_training" & n > 80) |
                       (phase == "acquisition_testing" & n > 8) |
                       (phase == "extinction_training" & n > 80) |
                       (phase == "extinction_testing" & n > 8) ~ "excess", 
                     (phase == "acquisition_training" & n < 80) |
                       (phase == "acquisition_testing" & n < 8) |
                       (phase == "extinction_training" & n < 80) |
                       (phase == "extinction_testing" & n < 8) ~ "partial")) %>%
  ungroup() %>%
  select(-n) 

data_training_and_testing_completeness_temp %>%
  count(phase, complete_training_testing_data) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

data_training_and_testing_completeness <- data_training_and_testing_completeness_temp %>%
  pivot_wider(names_from = phase, 
              values_from = complete_training_testing_data,
              names_prefix = "completeness_")

```

## Performance

```{r}

data_training_and_testing_performance_temp <- data_training_and_testing_input %>%
  # in this study, extinction was merely the presentation of stimuli on screen with no responses, so no performance metrics needed
  filter(phase != "extinction_training") %>%
  # summarize performance by block
  group_by(subject, phase, block_number) %>% 
  summarise(mean_correct = mean(correct), 
            sd_correct = sd(correct)) %>%
  mutate(passed_performance_criterion_by_block = ifelse(mean_correct < .75, FALSE, TRUE)) %>%
  ungroup() %>% 
  # summarize performance by participant (final block only)
  group_by(subject, phase) %>% 
  mutate(passed_performance_criterion = ifelse(block_number == max(block_number) & passed_performance_criterion_by_block == TRUE, TRUE, FALSE)) %>%
  ungroup() %>%
  mutate(phase = fct_relevel(phase,
                             "extinction_testing",
                             "extinction_training",
                             "acqusitiion_testing",
                             "acqusitiion_training")) %>%
  drop_na()

# plot
data_training_and_testing_performance_temp %>% 
  group_by(phase, block_number, passed_performance_criterion_by_block) %>% 
  summarise(mean_accuracy = mean(mean_correct), sd_accuracy = sd(sd_correct)) %>%
  ggplot(aes(x=block_number, y=mean_accuracy, fill = passed_performance_criterion_by_block)) +
  geom_bar(colour="black", stat="identity", position = position_dodge()) + 
  geom_errorbar(aes(ymin=mean_accuracy-sd_accuracy, ymax=mean_accuracy+sd_accuracy), width=.2,
                position=position_dodge(.9)) + theme_classic() +
  facet_wrap(~phase, ncol = 1)

data_training_and_testing_performance <- data_training_and_testing_performance_temp %>%
  group_by(subject, phase) %>% 
  filter(block_number == max(block_number)) %>%
  ungroup() %>%
  select(-block_number, -passed_performance_criterion_by_block, -sd_correct) %>%
  pivot_wider(names_from = phase,
              values_from = c(mean_correct, passed_performance_criterion))

```

- NB because the last block each participant completes is selected, if participants have partial data, their means refer to their last completed block not the ultimate block. therefore ensure that partial data exclusions are done.

# Self-reports

```{r}

data_demand <- read_xlsx("raw/demand.xlsx") %>% 
  mutate(demand_response = case_when(Demand_response == "What I learned during the experiment" ~ "Not Demand Compliant",
                                     Demand_response == "I don't know why I evaluated the items as I did" ~ "Not Demand Compliant",
                                     Demand_response == "What I learned during the experiment" ~ "Not Demand Compliant",
                                     Demand_response == "What I thought the experimenter wanted me to say" ~ "Demand Compliant",
                                     Demand_response == "I based my ratings on some some factor that was not what I learned or what the experimenter wanted me to do" ~ "Not Demand Compliant")) %>%
  select(subject, demand_response)

data_reactance <- read_xlsx("raw/reactance.xlsx") %>% 
  select(subject, 
         reactance_response_1 = react1_response, 
         reactance_response_2 = react2_response) %>%
  mutate(reactance_response_2 = str_remove_all(reactance_response_2, "[^0-9]"))

data_believability <- read_xlsx("raw/cover_belief.xlsx") %>% 
  select(subject, 
         believability_response_1 = belief1_response, 
         believability_response_2 = belief2_response) %>%
  mutate(believability_response_2 = str_remove_all(believability_response_2, "[^0-9]"))

data_confidence_ratings <- read_xlsx("raw/confidence_ratings.xlsx") %>% 
  select(subject, 
         confidence_stim_1 = Stimulus_1_Confidence_Confidence_response, 
         confidence_stim_2 = Stimulus_2_Confidence_Confidence_response, 
         confidence_stim_3 = Stimulus_3_Confidence_Confidence_response, 
         confidence_stim_4 = Stimulus_4_Confidence_Confidence_response)

data_ratings <- read_xlsx("raw/valence_ratings.xlsx") %>% 
  select(subject, 
         Outcome_1_Pos_Neg = Stimulus_1_Positive_Negative_Positive_Negative_response,
         Outcome_1_Good_Bad = Stimulus_1_Good_Bad_Good_Bad_response,
         Outcome_1_Pleasant_Unpleasant = Stimulus_1_Pleasant_Unpleasant_Pleasant_Unpleasant_response,
         Outcome_1_Like_Dislike = Stimulus_1_Like_Dislike_Like_Dislike_response,
         Outcome_2_Pos_Neg = Stimulus_3_Positive_Negative_Positive_Negative_response,
         Outcome_2_Good_Bad = Stimulus_3_Good_Bad_Good_Bad_response, 
         Outcome_2_Pleasant_Unpleasant = Stimulus_3_Pleasant_Unpleasant_Pleasant_Unpleasant_response,
         Outcome_2_Like_Dislike = Stimulus_3_Like_Dislike_Like_Dislike_response,
         Target_1_Pos_Neg = Stimulus_2_Positive_Negative_Positive_Negative_response,
         Target_1_Good_Bad = Stimulus_2_Good_Bad_Good_Bad_response, 
         Target_1_Pleasant_Unpleasant = Stimulus_2_Pleasant_Unpleasant_Pleasant_Unpleasant_response,
         Target_1_Like_Dislike = Stimulus_2_Like_Dislike_Like_Dislike_response,
         Target_2_Pos_Neg = Stimulus_4_Positive_Negative_Positive_Negative_response,
         Target_2_Good_Bad = Stimulus_4_Good_Bad_Good_Bad_response,
         Target_2_Pleasant_Unpleasant = Stimulus_4_Pleasant_Unpleasant_Pleasant_Unpleasant_response,
         Target_2_Like_Dislike = Stimulus_4_Like_Dislike_Like_Dislike_response) %>% 
  # Create a mean rating score for each stimulus
  # Create an operant evaluative conditioning (OEC) and intersecting regularites (IR) effect
  rowwise() %>%
  mutate(mean_outcome_1 = mean(c(Outcome_1_Pos_Neg, Outcome_1_Good_Bad, Outcome_1_Pleasant_Unpleasant, Outcome_1_Like_Dislike)),
         mean_outcome_2 = mean(c(Outcome_2_Pos_Neg, Outcome_2_Good_Bad, Outcome_2_Pleasant_Unpleasant, Outcome_2_Like_Dislike)),
         mean_target_1  = mean(c(Target_1_Pos_Neg, Target_1_Good_Bad, Target_1_Pleasant_Unpleasant, Target_1_Like_Dislike)),
         mean_target_2  = mean(c(Target_2_Pos_Neg, Target_2_Good_Bad, Target_2_Pleasant_Unpleasant, Target_2_Like_Dislike)),
         OEC_effect     = mean_outcome_1 - mean_outcome_2,
         IR_effect      = mean_target_1 - mean_target_2) %>%
  ungroup() %>%
  select(subject, OEC_effect, IR_effect)

# behavioural intentions
data_intentions <- 
  full_join(read_xlsx("raw/intention_ratings_1_3.xlsx") %>%
              select(subject, intentions_response_1_3 = Intentions_1_3_response),
            read_xlsx("raw/intention_ratings_2_4.xlsx") %>%
              select(subject, intentions_response_2_4 = Intentions_2_4_response),
            by = "subject")

```

# IAT

## Tidying

```{r}

data_iat_input <- 
  bind_rows(
    read_xlsx("raw/iat_symbols_before.xlsx") %>%
      mutate(task_order = "iat before explicits",
             response = as.character(response)),
    read_xlsx("raw/iat_symbols_after.xlsx") %>%
      mutate(task_order = "iat after explicits",
             response = as.character(response))
  ) %>%
  mutate(experiment = current_experiment_number) %>%
  select(subject, experiment, 
         block_type = blockcode, block = blocknum, trial_number = trialnum, 
         correct, latency) %>%
  # trial_number on blocks 3 and 7 begins on 2: correct to begin at 1
  mutate(trial_number = ifelse(block %in% c(1, 2, 3, 6, 7), trial_number-1, trial_number)) %>%
  # the number of the blocks is incorrect due to the way the task was coded, recode
  mutate(block = case_when(block == 1 ~ 1,
                           block == 2 ~ 2,
                           block == 3 ~ 3,
                           block == 5 ~ 4,
                           block == 6 ~ 5,
                           block == 7 ~ 6,
                           block == 9 ~ 7))

# block order
data_iat_block_order <- data_iat_input %>%
  filter(block == 1 & trial_number == 1) %>%
  mutate(iat_block_order = case_when(block_type == "targetincompatiblepractice" ~ "learning_inconsistent_first",
                                     block_type == "targetcompatiblepractice" ~ "learning_consistent_first")) %>%
  select(subject, iat_block_order)

# only retain the critical practice and test blocks (i.e., block_number = 3, 4, 6, 7)
data_iat_cleaned <- data_iat_block_order %>%
  left_join(data_iat_input, by = "subject") %>% 
  filter(block %in% c(3, 4, 6, 7))

```

## Completeness

```{r}

data_iat_completeness <- data_iat_cleaned %>%
  group_by(subject) %>%
  summarize(n = n()) %>%
  mutate(complete_iat_data = case_when(n == 120 ~ "complete", 
                                       n > 120 ~ "excess", 
                                       n < 120 ~"partial")) %>%
  ungroup() %>%
  select(-n)

data_iat_completeness %>%
  distinct(subject, .keep_all = TRUE) %>%
  count(complete_iat_data) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

## Performance

```{r}

# exclude if total error rate > 30% 
data_iat_accuracy_overall <- data_iat_cleaned %>% 
  group_by(subject) %>% 
  summarise(iat_accuracy_overall = sum(correct)/n()) %>%
  ungroup() %>%
  mutate(passed_iat_accuracy_overall = ifelse(iat_accuracy_overall >= .70, TRUE, FALSE)) %>%
  select(subject, passed_iat_accuracy_overall)

# exclude if error rate on any one block > 40% 
data_iat_accuracy_by_block <- data_iat_cleaned %>% 
  group_by(subject, block) %>% 
  summarise(iat_accuracy_by_block = sum(correct)/n()) %>%
  ungroup() %>%
  mutate(passed_iat_accuracy_by_block = ifelse(iat_accuracy_by_block >= .60, TRUE, FALSE)) %>%
  group_by(subject) %>%
  summarize(passed_iat_accuracy_by_block = as.logical(min(passed_iat_accuracy_by_block))) %>%
  ungroup()

data_iat_fast_responding <- data_iat_cleaned %>% 
  mutate(fast_response = ifelse(latency < 300, 1, 0)) %>%
  group_by(subject) %>% 
  summarise(iat_percent_fast_responses = sum(fast_response)/n()) %>%
  ungroup() %>%
  mutate(passed_iat_percent_fast_responses = ifelse(iat_percent_fast_responses <= .10, TRUE, FALSE)) %>%
  select(subject, passed_iat_percent_fast_responses)

data_iat_performance <- data_iat_accuracy_overall %>%
  full_join(data_iat_accuracy_by_block, by = "subject") %>%
  full_join(data_iat_fast_responding, by = "subject") %>%
  rowwise() %>%
  mutate(passed_iat_performance = as.logical(min(c(passed_iat_accuracy_overall, 
                                                   passed_iat_accuracy_by_block,   
                                                   passed_iat_percent_fast_responses), na.rm = TRUE))) %>%
  ungroup() %>%
  select(subject, passed_iat_performance)

rm(data_iat_accuracy_overall, data_iat_accuracy_by_block, data_iat_fast_responding)

```

## D2 scoring

```{r}

data_iat_D2_scores <- data_iat_cleaned %>%
  # rename and recode to create the input format that the IATscores package requires
  mutate(praccrit = ifelse(block_type == "incompatibletest1" | block_type == "compatibletest1", 
                           "prac", "crit"),
         blockcode = ifelse(block_type == "incompatibletest1" | block_type == "incompatibletest2",
                            "incompatible_block", "compatible_block")) %>%
  select(subject, block, correct, latency, praccrit,  trial_number, block_type) %>%
  mutate(blockcode = ifelse(block %in% c(3, 4), "pair1", 
                            ifelse(block %in% c(6, 7), "pair2", NA)),
         praccrit = ifelse(block %in% c(3, 6), "prac", 
                           ifelse(block %in% c(4, 7), "crit", NA)))  %>%
  filter(!is.na(blockcode)) %>%
  # calculate D2 scores
  # parameters are identical to those the package lists in the D2 wrapper function
  IATscores::RobustScores(IATdata = .,
                          P1 = "fxtrim",  # Trim values < 400ms
                          P2 = "ignore",  # do not trim errors
                          P3 = "dscore",  # calculate d2 scores
                          P4 = "dist",    # distinguish between the prac and test blocks
                          verbose = FALSE,
                          autoremove = FALSE) %>%
  rename(IAT_D2_controlling_stimulus_identity = p2112) 

```

# Combine and write to disk

```{r}

data_processed <- data_conditions %>%
  full_join(data_demographics, by = "subject") %>%
  full_join(data_training_and_testing_completeness, by = "subject") %>%
  full_join(data_training_and_testing_performance, by = "subject") %>%
  full_join(data_ratings, by = "subject") %>%
  full_join(data_iat_block_order, by = "subject") %>%
  full_join(data_iat_completeness, by = "subject") %>%
  full_join(data_iat_performance, by = "subject") %>%
  full_join(data_iat_D2_scores, by = "subject") %>%
  full_join(data_intentions, by = "subject") %>%
  full_join(data_demand, by = "subject") %>%
  full_join(data_reactance, by = "subject") %>%
  full_join(data_confidence_ratings, by = "subject") %>%
  full_join(data_believability, by = "subject") %>%
  # reverse-score the scores the self-reports based on stimulus_identity_condition
  mutate(
    OEC_effect_controlling_stimulus_identity = case_when(
      stimulus_identity_condition == "Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good" ~ OEC_effect*-1,
      stimulus_identity_condition == "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad" ~ OEC_effect
    ),
    IR_effect_controlling_stimulus_identity = case_when(
      stimulus_identity_condition == "Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good" ~ IR_effect*-1,
      stimulus_identity_condition == "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad" ~ IR_effect
    )
  ) %>%
  # reverse score IAT so that a positive IAT score indicates that people preferred the Target that was related to the Positive Source more than the Target related to the Negative source and vice versa
  mutate(
    IAT_D2 = case_when(
      stimulus_identity_condition == "Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good" ~ IAT_D2_controlling_stimulus_identity*-1, 
      stimulus_identity_condition == "Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad" ~ IAT_D2_controlling_stimulus_identity
    )
  ) %>%
  select(experiment, 
         subject, 
         age, 
         gender, 
         stimulus_identity_condition, 
         experiment_condition, 
         task_order, 
         completeness_acquisition_testing, completeness_acquisition_training, 
         completeness_extinction_testing, completeness_extinction_training, 
         mean_correct_acquisition_training, mean_correct_acquisition_testing, 
         mean_correct_extinction_testing, 
         # mean_correct_extinction_training, 
         passed_performance_criterion_acquisition_training, passed_performance_criterion_acquisition_testing, 
         passed_performance_criterion_extinction_testing, passed_performance_criterion_extinction_training, 
         OEC_effect, OEC_effect_controlling_stimulus_identity, 
         IR_effect, IR_effect_controlling_stimulus_identity, 
         complete_iat_data, 
         iat_block_order,
         passed_iat_performance,
         IAT_D2, IAT_D2_controlling_stimulus_identity, 
         intentions_response_1_3, intentions_response_2_4,
         demand_response, 
         reactance_response_1, reactance_response_2, 
         confidence_stim_1, confidence_stim_2, confidence_stim_3, confidence_stim_4,
         believability_response_1, believability_response_2)

# Ensures that the processed data folder exists
dir.create("processed")

# write to disk
write_csv(data_processed, "processed/data_processed.csv")

```



