---
title: "Study 7: Counterconditioning or Extinction Phase"
author: "Sean Hughes"
date: "30-5-2020"
output: 
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes 
    toc_float: yes
---

```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE)
```


# Load the necessary packages

```{r}
library(foreign)
library(tidyverse)
library(Hmisc)
library(car)
library(readxl)
library(ggthemes)
library(xlsx)
```

## 1. Import the raw data files from Excel into R

```{r}

getwd()

wd <- list()
wd$data_AQ   <- "C:/Users/Sean/Desktop/Intersecting_Regularties_/Study 7/Raw_Data/1_Acquisition_Only_Data/"
wd$data_CC   <- "C:/Users/Sean/Desktop/Intersecting_Regularties_/Study 7/Raw_Data/2_Counterconditioning_Data/"
wd$data_EX   <- "C:/Users/Sean/Desktop/Intersecting_Regularties_/Study 7/Raw_Data/3_Extinction_Data/"

wd$output <- "C:/Users/Sean/Desktop/Intersecting_Regularties_/Study 7/Processed_Data/"

# Counterconditioning Group Data

raw_data_CC_1 <- read_xlsx(paste0(wd$data_CC, "counterconditioning1b_no_location_raw.xlsx"), col_names = TRUE)
raw_data_CC_2 <- read_xlsx(paste0(wd$data_CC, "counterconditioning2b_no_location_raw.xlsx"), col_names = TRUE)
  
# Extinction Group Data

raw_data_EX_1 <- read_xlsx(paste0(wd$data_EX, "extinction_1c_no_location_19_04_05.xlsx"), col_names = TRUE)
raw_data_EX_2 <- read_xlsx(paste0(wd$data_EX, "extinction_2c_no_location_19_04_05.xlsx"), col_names = TRUE)


```

## 2. Join the training files together

```{r}

processed_data_CC_1 <- raw_data_CC_1 %>% 
  filter(blockcode != "Begin") %>% 
  select(subject, blocknum, trialnum, correct) %>%
  mutate(training_condition = "Counterconditioning")

processed_data_CC_2 <- raw_data_CC_2 %>% 
  filter(blockcode != "Begin") %>% 
  select(subject, blocknum, trialnum, correct) %>%
  mutate(training_condition = "Counterconditioning")

processed_data_EX_1 <- raw_data_EX_1 %>% 
  filter(blockcode != "Begin") %>% 
  select(subject, blocknum, trialnum, correct) %>%
  mutate(training_condition = "Extinction")

processed_data_EX_2 <- raw_data_EX_2 %>% 
  filter(blockcode != "Begin") %>% 
  select(subject, blocknum, trialnum, correct) %>% 
  mutate(training_condition = "Extinction")

combined_data <- processed_data_CC_1 %>% 
  bind_rows(processed_data_CC_2, processed_data_EX_1, processed_data_EX_2) %>%
  rename(block_number = blocknum, trial_number = trialnum) %>% 
  arrange(subject)
  

```

## 3. Exclude participants with incomplete data

```{r}

# Number of participants before exclusions

Participants_before_exclusions <- combined_data %>% 
  distinct(subject, training_condition) %>% 
  count()

# Check to see if everyone has complete data for the four training blocks - if block_number = 280 then they do. Otherwise they do not. If they do not then remove them 

combined_data <- combined_data %>%
  group_by(subject, training_condition) %>% 
  mutate(complete_data_check = sum(block_number)) %>%
  filter(complete_data_check == 200 | complete_data_check == 300 | complete_data_check == 440 | complete_data_check == 600) %>%
  ungroup() 

# Number of participants post exclusions

Participants_after_exclusions <- combined_data %>% 
  distinct(subject, training_condition) %>% 
  count()


```

## 4. Calculating Mean and SD of Accuracy across blocks as a function of experimental condition

```{r}

# Calculate mean and SD for accuracy (i.e., the correct row) 

summarised_data <- combined_data %>%
  group_by(subject, block_number, training_condition) %>% 
  summarise(mean_correct = mean(correct), sd_correct = sd(correct))%>%
  arrange(subject, block_number) %>%
  ungroup()

```

## 5. Identify those who passed (> 70%) OR failed (< 70%) the final block of the counterconditioning or extinction phase 

```{r}

# Step 1: Identify those that passed or failed counterconditioning or extinction
Pass_Fail_Group <- summarised_data %>%
  group_by(subject, training_condition) %>%
  slice_tail() %>%
  mutate(training_performance = ifelse(mean_correct < .70, "Fail", "Pass"),
         block_type = "Manipulation_Phase") %>%
  ungroup()

# Step 2: Add the training performance (Fail/Pass) information to the entire data

summarised_data <- summarised_data %>% 
  full_join(Pass_Fail_Group, by = c("subject" = "subject", "block_number" = "block_number", "training_condition" = "training_condition")) %>%
  select(-mean_correct.y, -sd_correct.y) %>%
  rename(mean_correct = mean_correct.x,  sd_correct = sd_correct.x) %>%
  mutate(block_type = "Manipulation_Phase") %>%
  group_by(subject, training_condition) %>%
  fill(training_performance, .direction = "up") %>%
  ungroup()

```


## 6. Graph accuracy in the final block for those who passed vs. failed in the counterconditioning and extinction conditions

```{r}

# Calculate  Mean and SD of accuracy for the FINAL training block in each experimental condition
  data_for_graph <- Pass_Fail_Group %>% 
    group_by(training_condition, training_performance) %>% 
    summarise(mean_accuracy = mean(mean_correct), sd_accuracy = sd(sd_correct)) %>%
    ungroup()

# Graph Mean and SD accuracy across blocks
ggplot(data_for_graph, aes(x=training_condition, y=mean_accuracy, fill = training_performance)) +
    geom_bar(colour="black", stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin=mean_accuracy-sd_accuracy, ymax=mean_accuracy+sd_accuracy), width=.2,
                 position=position_dodge(.9)) + theme_classic()

```

## 7. Write the data to file

```{r}
#Write data back to disk in csv format.

write_csv2(Pass_Fail_Group, path = paste0(wd$output, "Study_7_Counterconditioning_Extinction_Phase.csv"))

```



