---
title: "Study 7: Testing Phase (2)"
author: "Sean Hughes"
date: "30-5-2020"
output: 
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes 
    toc_float: yes
---

```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE)
```


# Load the necessary packages

```{r}
library(ggthemes)
library(foreign)
library(tidyverse)
library(Hmisc)
library(car)
library(readxl)
library(ggplot2)
library(dplyr)
library(xlsx)
```

## 1. Import the raw data files from Excel into R

```{r}

getwd()

wd <- list()
wd$data_AQ   <- "C:/Users/Sean/Desktop/Intersecting_Regularties_/Study 7/Raw_Data/1_Acquisition_Only_Data/"
wd$data_CC   <- "C:/Users/Sean/Desktop/Intersecting_Regularties_/Study 7/Raw_Data/2_Counterconditioning_Data/"
wd$data_EX   <- "C:/Users/Sean/Desktop/Intersecting_Regularties_/Study 7/Raw_Data/3_Extinction_Data/"

wd$output <- "C:/Users/Sean/Desktop/Intersecting_Regularties_/Study 7/Processed_Data/"

# Counterconditioning Group Data

raw_data_CC_1 <- read_xlsx(paste0(wd$data_CC, "testing_counterconditioning1b_nokeylocation_raw.xlsx"), col_names = TRUE)
raw_data_CC_2 <- read_xlsx(paste0(wd$data_CC, "testing_counterconditioning2b_nokeylocation_raw.xlsx"), col_names = TRUE)
  
# Extinction Group Data

raw_data_EX_1 <- read_xlsx(paste0(wd$data_EX, "testing_extinction1c_nokeylocation_19_04_05.xlsx"), col_names = TRUE)
raw_data_EX_2 <- read_xlsx(paste0(wd$data_EX, "testing_extinction2c_nokeylocation_19_04_05.xlsx"), col_names = TRUE)

```

## 2. Join the testing files together

```{r}

processed_data_CC_1 <- raw_data_CC_1 %>% 
  filter(blockcode != "Begin") %>% 
  select(subject, trialnum, correct) %>%
  mutate(training_condition = "Counterconditioning")

processed_data_CC_2 <- raw_data_CC_2 %>% 
  filter(blockcode != "Begin") %>% 
  select(subject, trialnum, correct) %>%
  mutate(training_condition = "Counterconditioning")

processed_data_EX_1 <- raw_data_EX_1 %>% 
  filter(blockcode != "Begin") %>% 
  select(subject, trialnum, correct) %>%
  mutate(training_condition = "Extinction")

processed_data_EX_2 <- raw_data_EX_2 %>% 
  filter(blockcode != "Begin") %>% 
  select(subject, trialnum, correct) %>%
  mutate(training_condition = "Extinction")

combined_data <- processed_data_CC_1 %>% 
  bind_rows(processed_data_CC_2, processed_data_EX_1, processed_data_EX_2) %>%
  rename(trial_number = trialnum) %>% 
  arrange(subject)

```

## 3. Exclude participants with incomplete data

```{r}

# Number of participants before exclusions

Participants_before_exclusions <- combined_data %>% 
  distinct(subject, training_condition) %>% 
  count()

Participants_before_exclusions

# Check to see if everyone has complete data for the four training blocks - if block_number = 280 then they do. Otherwise they do not. If they do not then remove them 

combined_data <- combined_data %>%
  group_by(subject, training_condition) %>% 
  mutate(complete_data_check = sum(trial_number)) %>%
  filter(complete_data_check == 36) %>%
  ungroup() 

# Number of participants post exclusions

Participants_after_exclusions <- combined_data %>% 
  distinct(subject, training_condition) %>% 
  count()

Participants_after_exclusions

```

## 4. Calculating Mean and SD of Accuracy for Test Block

```{r}

# Calculate mean and SD for accuracy (i.e., the correct row) 

summarised_data <- combined_data %>%
  group_by(subject, training_condition) %>% 
  summarise(mean_correct = mean(correct), sd_correct = sd(correct))%>%
  arrange(subject) %>%
  ungroup()

```

## 5. Identify those who passed (> 70%) OR failed (< 70%) the test block 

```{r}

# Step 1: Identify those that passed or failed the testing block
Pass_Fail_Group <- summarised_data %>%
  group_by(subject, training_condition) %>%
  mutate(training_performance = ifelse(mean_correct < .70, "Fail", "Pass"),
         block_type = "Test_2") %>%
  ungroup()

```


## 6. Graph accuracy for test block for those who passed vs. failed in the counterconditioning and extinction conditions

```{r}

# Calculate  Mean and SD for accuracy for testing block for each experimental condition
  data_for_graph <- Pass_Fail_Group %>% 
    group_by(training_performance, training_condition) %>% 
    summarise(mean_accuracy = mean(mean_correct), sd_accuracy = sd(sd_correct))

# Graph Mean and SD accuracy across blocks
ggplot(data_for_graph, aes(x=training_condition, y=mean_accuracy, fill = training_performance)) +
    geom_bar(colour="black", stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin=mean_accuracy-sd_accuracy, ymax=mean_accuracy+sd_accuracy), width=.2,
                 position=position_dodge(.9)) + theme_classic()

```

## 7. Write the data to file

```{r}
#Write data back to disk in csv format.

write_csv2(Pass_Fail_Group, path = paste0(wd$output, "Study_7_Test_Phase_2.csv"))


```